An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-07 poly-embed-journal/poly-embed-journal.tex
1 -> 2, 2-> 3 pulled out separately in Prop 7

$1 \Rightarrow 2, 3$:
Since $\Gamma$ embeds a finite property $\gamma$ with minimum representative set $\Sc$, $\Gamma$ also has a finite minimum representative set $\U := \varphi(\Sc)$. (3).

For (2), we claim $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\}$, and the result follows from $\U$ being a finite minimum representative set.
Since $\U$ is a finite minimum representative set, $\trimnonred(\Gamma) \supseteq \{\Gamma_u \mid u \in \U\}$ follows immediately.
We now show $\trimnonred(\Gamma) \subseteq \{\Gamma_u \mid u \in \U\}$.
Consider any $\Gamma_{u'} \in \trimnonred(\Gamma)$.
Since $\Gamma$ has the finite minimum representative set $\U$, if $u' \not \in \U$, there is some $u \in \U$ such that $\Gamma_{u'} \subseteq \Gamma_u$ by Lemma~\ref{lem:finite-minrep-weakly-dominate}. 
If $\Gamma_{u'} \subsetneq \Gamma_u$, then $u' \not \in \U_\equiv$, and $\Gamma_{u'} \not \in \trimnonred(\Gamma)$ nor is $u' \in \U$.
If $\Gamma_{u'} = \Gamma_u$, then$u' \equiv u$ so $\Gamma_{u'} \in \trimnonred(\Gamma)$ as $[u'] = [u] \in \U_\equiv$.
Thus, we have $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\}$, so $\trimnonred(\Gamma)$ is finite and unions to the simplex.

%$2 \Rightarrow 3$:
$3 \Rightarrow 1$:
Consider the loss $\ell := L|_\U$.
$\ell$ is a finite loss since $\U$ is finite, and by Corollary~\ref{cor:representative-embeds-restriction}, $L$ embeds $\ell$.
As a corollary of the loss embedding condition, we have $\Gamma$ embeds $\gamma := \prop{\ell}$.

>>>>

$1 \Rightarrow 2$:
Since $\Gamma$ embeds a finite property $\gamma$ with minimum representative set $\Sc$, $\Gamma$ also has a finite minimum representative set $\U := \varphi(\Sc)$.
We claim $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\} = \{\gamma_r \mid r \in \Sc \}$, and the result follows from $\U$ being a finite minimum representative set.
Since $\U$ is a finite minimum representative set, $\trimnonred(\Gamma) \supseteq \{\Gamma_u \mid u \in \U\}$ follows immediately.
We now show $\trimnonred(\Gamma) \subseteq \{\Gamma_u \mid u \in \U\}$.
Consider any $\Gamma_{u'} \in \trimnonred(\Gamma)$.
Since $\Gamma$ has the finite minimum representative set $\U$, if $u' \not \in \U$, there is some $u \in \U$ such that $\Gamma_{u'} \subseteq \Gamma_u$ by Lemma~\ref{lem:finite-minrep-weakly-dominate}. 
If $\Gamma_{u'} \subsetneq \Gamma_u$, then $u' \not \in \U_\equiv$, and $\Gamma_{u'} \not \in \trimnonred(\Gamma)$ nor is $u' \in \U$.
If $\Gamma_{u'} = \Gamma_u$, then$u' \equiv u$ so $\Gamma_{u'} \in \trimnonred(\Gamma)$ as $[u'] = [u] \in \U_\equiv$.
Thus, we have $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\}$, so $\trimnonred(\Gamma)$ is finite and unions to the simplex.

$2 \Rightarrow 3$:
Since $\trimnonred(\Gamma)$ is finite and covers the simplex, we have $\U_\equiv$ finite.
Consider any set $\U = \{u \mid [u] \in \U_\equiv\}$ to be a selection of elements of $\U_\equiv$ from each equivalence class.
We claim $\{\Gamma_u \mid u \in \U_\equiv\} = \{\Gamma_u \mid u \in \U\}$, and the result follows immediately.
Since $\U$ is generated by selecting elements of $\U_\equiv$, we have $\{\Gamma_u \mid u \in \U_\equiv\} \supseteq \{\Gamma_u \mid u \in \U\}$ by construction.
To see $\{\Gamma_u \mid u \in \U_\equiv\} \subseteq \{\Gamma_u \mid u \in \U\}$, consider any $u \in \U_\equiv$.
If $u \in \U$, the result follows immediately.
If $u \not \in \U$, then we know there is no report in $u' \in \U$ such that $\Gamma_{u} \subsetneq \Gamma_{u'}$ by virtue of $u \in \U_\equiv$, so we must have some $u' \in \U$ such that $\Gamma_u = \Gamma_{u'}$.
Therefore, $u \equiv u'$, so $\Gamma_u = \Gamma_{u'} \in \{\Gamma_{u'} \mid u' \in \U\}$.
Thus, there is a finite minimum representative set $\U$ such that $\trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\}$.

$3 \Rightarrow 1$:
Consider the loss $\ell := L|_\U$.
$\ell$ is a finite loss since $\U$ is finite, and by Corollary~\ref{cor:representative-embeds-restriction}, $L$ embeds $\ell$.
As a corollary of the loss embedding condition, we have $\Gamma$ embeds $\gamma := \prop{\ell}$.
